\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-09-17 doc/USER_MANUAL/04_creating_databases.tex
suppressed FULL_ATTENUATION_SOLID from the users manual

\item [{\texttt{FULL\_ATTENUATION\_SOLID}}] Set to \texttt{.true.} to add
$Q_{\kappa}$ attenuation to the simulations in addition to $Q_{\mu}$
attenuation when the \texttt{ATTENUATION} flag above is on. Should
be off in almost all cases for seismic wave propagation, since $Q_{\kappa}$
is almost always negligible in Earth models. However, this parameter
can be useful for instance for ocean acoustics simulations, when $Q_{\kappa}$
is not negligible in the solid layer at the sea bottom.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp. To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

>>>>

Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.
